\Large \bf \projtitle

### 2015-05-07 doc/paper/paper.tex
wrote DOM Injection Layer

\subsection{DOM injection layer}
% Ankush

@@

\subsection{Automatic conversion to \zbf}
Developers can integrate their sites to use \zbf by adding attribute tags to
the site resources they wish to be distributed using the system. However, sites feature
dozens of resources; as a result, adapting a site to use \zbf could present a
burden on the developer. If we were to provide a script that developers could use
to change HTML such that all resources were loaded using \zbf, this would ease
integration pains.

>>>>

\subsection{DOM injection layer}
The DOM injection layer facilitates the link between the DOM as displayed in the browser and the entire peer-to-peer system. The DOM injection layer creates a websocket, and then instantiates a Tracker and Signaling Channel. It uses these to then instantiate a Connection Manager and in turn, uses this to instantiate a Download Manager.

The DOM injection layer then iterates through all the DOM elements with the \texttt{data-zf-hash} and \texttt{data-zf-fallback} attributes. It the values of these attributes to fetch the data via the Download Manager. Upon receiving the data for each web element, the DOM injection layer creates an in-memory Blob and generates URL for this object. It then obeys the following rules, which can easily be expanded to support other DOM elements:

\begin{description}
\item[Script elements] have the \texttt{type} of their Blob set to \texttt{text/javascript}. They then have their \texttt{src} attribute set to the URL of the in-memory Blob.
\item[Link elements] have the \texttt{type} of their Blob set to \texttt{text/css}. They then have their \texttt{href} attribute set to the URL of the in-memory Blob, and \texttt{rel} attribute set to \texttt{stylesheet}.
\item[All other elements] have the \texttt{type} of their Blob set to \texttt{application/octet-stream}. They then have their \texttt{src} attribute set to the URL of the in-memory Blob. As most browsers can intelligently determine the content of \texttt{application/octet-stream} data, this functions properly for Image nodes, and serves as the generic template for any other node.
\end{description}

@@

\subsection{Automatic conversion to \zbf}
Developers can integrate their sites to use \zbf by adding attribute tags to
the site resources they wish to be distributed using the system. However, sites feature
dozens of resources; as a result, adapting a site to use \zbf could present a
burden on the developer. If we were to provide a script that developers could use
to change HTML such that all resources were loaded using \zbf, this would ease
integration pains and increase adoption.
